\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{color}
\usepackage{lipsum}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{fancyhdr}
\usepackage[T1]{fontenc}
\usepackage{fourier}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{xcolor}
\graphicspath{ {images/} }
% document size parameters

\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{8.4in}
\setlength{\textwidth}{6.5in}
\setlength{\voffset}{-0.40in}
\setlength{\headsep}{26pt}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}

% header information
\pagestyle{fancyplain}
\lhead{\large{{\bf POLI 123 Political Psychology} }}
\rhead{\large{{\bf Foundations}}}
\title{Do we make good decisions? (Bounded rationality)}
\author{Ramiro Gonzalez }
\date{}
\begin{document}

\maketitle

\section*{Kinds of thinking}
\begin{itemize}
    \item Automatic System: 
    \begin{itemize}
        \item No conscious though.  $(1 + 2) = ?$ 
        \item Something is happening, your brain reacts. 
        \item Automatics system determines whether the person is confident, well groomed, done withing milliseconds. 
    \end{itemize}
    \item Reflective / Deliberative system. 
    \begin{itemize}
        \item More rational. 
        \item More complex problems, spend more time and effort. $6/2(1+2)=?$
        \item Activities that are practiced frequently they can become automatic. Less brain power. 
    \end{itemize}
    \item \textbf{The brain has a lot to manage} The brain must determine where to focus. Bandwidth is finite, where can you cut corners? What shortcuts can one take? Allocating mental bandwidth. Automatic system process less important information. 
    \item How the brain takes shortcuts?
    \begin{itemize}
        \item Shortcuts can determine how one makes decisions. This can lead to irrational decisions. 
        \item One is not aware of the shortcuts. 
        \item it was once believed that humans where rational. It was proven to be wrong. 
    \end{itemize}
    \item Questions
    \begin{enumerate}
        \item 5, 2
    \end{enumerate}
\end{itemize}
\section*{Heuristics and Biases}
\begin{enumerate}
    \item \textbf{Anchoring}, There are primed questions that influence how one answers questions. 
    \item Open ended questions. Opinions change on how questions are framed. Keywords can change a persons opinion. 
    \item Vague questions receive vague answers. 
    \item \textbf{Availability }(What is sensational) Homicide are magnified by the media and are overestimated. Information that is the most obvious influences views. 
    \item What percent of people think they're in the middle class. 70\% . 
    \item \textbf{Optimism } and overconfidence. Humans are optimist, they believe the odds are in their favor. 
    \item \texbf{Status quo bias }: Amazon prime gives great deals, such as unsubscribing when the deal is over. 
    \item \textbf{Framing Effects } How an issue is presented may influence views. 
    \item \textbf{ More sensitive to losses than gains} . Willing to take risks to not lose what I have. I prefer program D. X
\end{enumerate}
\section*{}
\begin{itemize}
    \item 
\end{itemize}
\end{document}










