\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{color}
\usepackage{lipsum}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{fancyhdr}
\usepackage[T1]{fontenc}
\usepackage{fourier}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{xcolor}
\graphicspath{ {images/} }
% document size parameters

\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{8.4in}
\setlength{\textwidth}{6.5in}
\setlength{\voffset}{-0.40in}
\setlength{\headsep}{26pt}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}

% header information
\pagestyle{fancyplain}
\lhead{\large{{\bf POLI 127} }}
\rhead{\large{{\bf Race, Gender, and Politics}}}
\title{Women, Power, And Politics}
\author{Ramiro Gonzalez }
\date{}
\begin{document}

\maketitle
\section*{Women in Politics?}
\begin{enumerate}
    \item Relatively new. 1970s and 1980s. Women movement in America. 
    \item How media, has historically limited or helped woman's movement. 
\end{enumerate}
\section*{Does race still matter?}
\begin{enumerate}
    \item Race can determine opportunities available. 
    \item Symbolically race involve words, ideas, and images that shape public attitudes and opinion. 
    \item When does race matter? When a group experiences advantages or disadvantages. 
    \item Different races compete, who gets supported? Was the black vote split? Who supports who? 
    \item Rural white voter, their life is changing, they grew up differently, opium crisis. 
    \item Becoming an adult where his identity is challenged, can not sympathize with rural white voter does not adapt to change. 
    \item Every group has taken a road, a path. Not included in a society. 
\end{enumerate}
\section*{Race}
\begin{enumerate}
    \item Macro-Categories. Cultural and Physical differences. Color of skin, hair, outer appearance. 
    \item "White because you are light skin"
    \item Racialization "You look, black, white, Mexican therefore you like to eat tacos, hamburger and fries, a certain beverage". Imposing attributes to a classified person. 
    \item Racism classifies and determines who receives full citizenship and opportunities. Because you are of a certain race you will be labeled and treated differently. 
    \item Racialization is not necessarily racism. 
    \item Jokes may seem racist, the line is blurred. 
\end{enumerate}
\section*{Superiority}
\begin{enumerate}
    \item White supremacy or nationalism. All other non white are second class or lesser. Learned throughout history, genocide of the jewish people by nazis in germany.\textbf{Racial superiority} Believe that a certain race is culturally, intellectual, or physically superior to others. 
    \item \textbf{Racial Assimilation} Marrying and because of difference forced to adopt a certain identity. 
    \item \textbf{Racial separation} Not allowed to intermarry or associate with each other.
    \item They all contribute to superiority. 
\end{enumerate}
\section*{Ethnicity}
\begin{enumerate}
    \item Mexican American, Italian American. Distinguish peoples based primarily on their cultural practices or national or regional ancestries. 
    \item \textbf{Pan-ethnic} identity is an ancestral connection to a region rather than to a specific nation. Such as Jewish. 
    \item Race and Ethnicity are different. 
\end{enumerate}
\section*{Race and Racism Today?}
\begin{enumerate}
    \item Who is getting neglected, is government in favor of one group? 
    \item How are the government systems working. 
    \item Is criminal justice system racist? 
    \item Agricultural subsidies, a particular group is hurting. A majority of farmers in the country are  white and they benefit, it enforces racial privilege. Minority women "Welfare queen" , spend welfare money on luxury, it is racialized, they use this to oppose welfare. Getting drug tested to get welfare. Corporate titans are white, male, and get billions of dollars in tax dollars, why do they not get tested? Why is that policy racialized. 
    \item \textbf{White privilege} Automatically inherit greater opportunities and more advantages than those afforded to racial or ethnic minorities. Who are the targets of goverment. Who benefits. 
\end{enumerate}
\section*{Racial Classification, Citizenship, Group Status}
\begin{enumerate}
    \item \textbf{Scientific racism} incorrect use of science to justify and explain racism. Who is superior ro inferior according to science.  
    \item \textbf{Miscegentaion} racial mixing was a problem. "Mulattoes"
    \item Statistical Policy Director No. 15 : Create classifications to allocate services. Race and ethnicity was integrated by the federal fovernment. 
    \item \textbf{Multiculturalism} "Melting pot" , some claim it errodes their cultural background. 
\end{enumerate}
\end{document}