\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{color}
\usepackage{lipsum}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{fancyhdr}
\usepackage[T1]{fontenc}
\usepackage{fourier}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{xcolor}
\graphicspath{ {images/} }
% document size parameters

\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{8.4in}
\setlength{\textwidth}{6.5in}
\setlength{\voffset}{-0.40in}
\setlength{\headsep}{26pt}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}

% header information
\pagestyle{fancyplain}
\lhead{\large{{\bf POLI 127} }}
\rhead{\large{{\bf Race, Gender, and Politics}}}
\title{Empathy \& Intersectionality}
\author{Ramiro Gonzalez }
\date{}
\begin{document}

\maketitle

\section*{Empathy}
Understanding what others go through. 
\begin{enumerate}
    \item Do you lack empathy?
    Looking out for your own interest. 
    \item Putting yourself in others shoes. 
    \item How to think act and feel as if you are others. 
    \item Empathy is a skill. 
    \item Actions towards others can make you feel different about others. 
\end{enumerate}
\section*{Sympathy vs Empathy}
\begin{enumerate}
    \item Closely related, sympathy is loaded with more meaning. 
    \item Sympathy refers "feeling of loyalty" or "unity or harmony in action or effect".
    \item Empathy is a new concept. 
    \item How do you express sympathy? 
        \begin{itemize}
            \item When love ones pass away. 
            \item Feeling sorry. Sympathy is naturally occurring.
            \item We do know what it feels like. 
        \end{itemize}
\end{enumerate}
\section*{Compassion and Empathy}
\begin{enumerate}
    \item Compassion refers to both an understanding of another pain and the desire to somehow mitigate that pain. 
    \begin{itemize}
        \item Offering others beer, beer is an coping mechanism. Getting into groups to mitigate the pain. 
    \end{itemize}
    \item Empathy refers to the ability to relate to another person's pain. 
        \begin{itemize}
            \item Not necessary the desire to mitigate that pain. 
        \end{itemize}
\end{enumerate}
\section*{Intersectionality}
\begin{enumerate}
    \item Experimentation. Finding a cause and effect. 
    \begin{itemize}
        \item Attitudes and opinions are influenced by many factors. 
        \item Ingroups and Outgroup.
        \item How we think of actions of women, transgender, or male. 
        \item Intersectionality disrupts scientific idea of isolating one thing. 
    \end{itemize}
    \item Labeling people. A person is seen is as Asian is associated to be Asian. 
    \item Not understanding intersectionality leads to labeling of others.
    \item Identifies can be brought upon on self or others. Identities refer to "father", "college
    
    graduate", some may be positive others may be negative. We seek identities. Newly gathered identities begin to react with underlying identities. Multiple identities. 
    \item Begin to explore different identities as more meaningful. 
\end{enumerate}
\end{document}
